`r paste(params$city, params$state, sep = ', ')`

### 2017-12-04 lib/report.Rmd
update reports
update report

```{r setup, echo = FALSE}
opts_chunk$set(echo = FALSE)

@@

```{r report, message=F, warning=F}
```

@@

@@

>>>>

```{r setup, echo = FALSE}
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

@@

```{r report}
```

@@

```{r by_year_by_day_of_week_plot, fig.height = 10}
by_year_by_day_of_week_plot
```

@@

```{r reason_for_stop_top_20_plot}
reason_for_stop_top_20_plot
```

Top 20 reasons for stop cumulative percentage: `r reason_for_stop_top_20_pct`

```{r search_conducted_plot}
search_conducted_plot
```

```{r search_types_plot}
search_types_plot
```

```{r contraband_found_plot}
contraband_found_plot
```

```{r contraband_found_by_race_plot}
contraband_found_by_race_plot
```

```{r citation_issued_plot}
citation_issued_plot
```

```{r arrest_made_plot}
arrest_made_plot
```
